%-------------------------
% Resume in Latex
% Author : Arian Bessonart
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

    \usepackage{latexsym}
    \usepackage[empty]{fullpage}
    \usepackage{titlesec}
    \usepackage{marvosym}
    \usepackage[usenames,dvipsnames]{color}
    \usepackage{verbatim}
    \usepackage{enumitem}
    \usepackage[pdftex]{hyperref}
    \usepackage{fancyhdr}


    \pagestyle{fancy}
    \fancyhf{} % clear all header and footer fields
    \fancyfoot{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}

    % Adjust margins
    \addtolength{\oddsidemargin}{-0.5in}
    \addtolength{\evensidemargin}{-0.5in}
    \addtolength{\textwidth}{1in}
    \addtolength{\topmargin}{-.5in}
    \addtolength{\textheight}{1.0in}

    \urlstyle{same}

    \raggedbottom
    \raggedright
    \setlength{\tabcolsep}{0in}

    % Sections formatting
    \titleformat{\section}{
      \vspace{-4pt}\scshape\raggedright\large
    }{}{1em}{}[\color{black}\titlerule \vspace{-5pt}]

    %-------------------------
    % Custom commands
    \newcommand{\resumeItem}[2]{
      \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
      }
    }

    \newcommand{\workItem}[1]{
      \item\small{
        { #1 \vspace{-2pt}}
      }
    }

    \newcommand{\resumeSubheading}[4]{
      \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
          \textbf{#1} & #2 \\
          \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
    }

    \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

    \renewcommand{\labelitemii}{$\circ$}

    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

    %-------------------------------------------
    %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


    \begin{document}

    %----------HEADING-----------------
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{{\Large Arian Bessonart}} & Email : \href{mailto:arianbessonart@gmail.com}{arianbessonart@gmail.com}\\
       & Mobile : (+598) 99 177 480 \\
    \end{tabular*}

    %-----------EDUCATION-----------------
    \section{Education}
      \resumeSubHeadingListStart
        \resumeSubheading
          {University, Facultad de Ingeniería, UDELAR}{Montevideo, UY}
          {Engineer's degree, Software, Computer Engineering}{2007 -- 2015}
      \resumeSubHeadingListEnd

    %-----------EXPERIENCE-----------------
    \section{Experience}
      \resumeSubHeadingListStart

      \resumeSubheading
        {Austin Software}{Montevideo, UY}
        {Technical Architect}{March 2019 - Present}
        \resumeItemListStart
          \workItem
          {Defines product requirements and creates high-level architectural specifications, ensuring feasibility and functionality with existing 10 platforms}
          \workItem{Creates solutions architecture, algorithms, and designs for solutions that scale to the customers' business requirements}
          \workItem
          {Developed and created a website builder. Node.js, React, Kubernetes, GCP}
        \resumeItemListEnd

        \resumeSubheading
          {Renxo}{Montevideo, UY}
          {Senior Developer}{Jan 2018 - March 2019}
          \resumeItemListStart
            \workItem
              {Maintaining and updating a CMS, which provides services subscription through multiple carriers in South America. It uses Java and tomcat to implement a RESTful API which is connected to by the front end which is a web application written in JavaScript and HTML5.}
          \resumeItemListEnd

        \resumeSubheading
          {PedidosYa}{Montevideo, UY}
          {Technical Leader}{Aug 2017 - Jan 2018}
          \resumeItemListStart
            \workItem
              {Service for management dinamically features. Has the purposes of hide, enable or disable the feature during run time. Golang, Node.js, React, Redis, AWS, Docker.}
          \resumeItemListEnd

        \resumeSubheading
          {PedidosYa}{Montevideo, UY}
          {Full-Stack Developer}{Dec 2016 - Aug 2017}
          \resumeItemListStart
            \workItem
              {Maintained, fine-tuned, and optimized system architecture through outstanding expertise in application installation, configuration, integration and administration.}
            \workItem
              {Implemented new features, given supports to the mobile applications and the website, through RESTful API. Grails, MySQL, Redis, Memcached.}
            \workItem{Closely monitored production systems to ensure consistently flawless performance.}
          \resumeItemListEnd

        \resumeSubheading
          {Binbit}{Montevideo, UY}
          {Java Lead Developer}{Dec 2014 - Dec 2016}
          \resumeItemListStart
            \workItem
              {Multithread system responsible for communication with carriers. Having as a priority to be fault tolerant and efficient, in order to perform a several daily operations. System Owner role. Java, Hibernate.}
            \workItem
              {Backoffice implementation. AngularJS, Java.}
            \workItem
              {Established and implemented robust development process, using CI/CD and code review practices.}
          \resumeItemListEnd

        \resumeSubheading
          {Binbit}{Montevideo, UY}
          {Backend Developer}{May 2013 - Dec 2014}
          \resumeItemListStart
            \workItem
              {Maintaince and extension of the most critics systems of the company. Python, PostgreSQL.}
          \resumeItemListEnd

        \resumeSubheading
          {Axxiome}{Montevideo, UY}
          {Java Developer}{Sept 2012 - May 2013}
          \resumeItemListStart
            \workItem
              {Electronic wallet, own by Sybase. The task consisted of extending the framework for clients purposes. Java, Spring, Oracle.}
            \workItem
              {Implemented bank mobile applications, using PhoneGap.}
          \resumeItemListEnd

        \resumeSubheading
          {Mvd Technlogies}{Montevideo, UY}
          {Junior Developer}{Aug 2011 - Sept 2012}
          \resumeItemListStart
            \workItem
              {Web developer using .NET technologies.}
          \resumeItemListEnd

      \resumeSubHeadingListEnd

    %-----------PROJECTS-----------------
    \section{Projects}
      \resumeSubHeadingListStart
        \resumeSubItem{\href{https://github.com/arianbessonart/pg-dev}{pg-dev}}
          {Open source atom plugin for PostgreSQL developers.}
      \resumeSubHeadingListEnd

    %--------PROGRAMMING SKILLS------------
    \section{Programming Skills}
     \resumeSubHeadingListStart
       \item{
         \textbf{Languages}{: Java, Javascript, Go, Python, SQL}
         \hfill
         \textbf{Technologies}{: AWS, Kubernetes, PostgreSQL, Docker}
       }
     \resumeSubHeadingListEnd
    %-------------------------------------------
    \end{document}
